Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-07 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Make some tweaks to the "5,000" plots for rain and distance

Map of the count of county exposures to the top 1000 county-storm pairs by distance-based exposure, based on "exposed" = distance of 100 kilometers or less [GBA-- These are **awesome**. I think we want to tweak the color scale and the legend a bit so that they're consistent between the three plots showing the top 1000 storm-county pairs for the three metrics (distance, rain, and wind). That will make it easier to compare across the three maps, which is what we want readers to be able to do here.]:

@@

distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) %>%
        arrange(desc(count)) %>%
        slice(1:1000)

distance_1000$value <- cut(distance_1000$count, c(0, 5, 8, 12, 15, 18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15", "16-18",
                                      "19-21", "22-24"),
                           include.lowest = TRUE)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits for top 1000 Storm-County Pairs\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 7,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 500,
                             days_include = c(-1, 0, 1))
rain_1000 <- rain_exposure %>%
        arrange(desc(tot_precip)) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) %>%
        arrange(desc(count)) %>%
        slice(1:1000)
rain_1000$value <- cut(rain_1000$count, c(0, 3, 6, 9, 12, 15, 17), 
                   labels = c("0-3", "4-6", "7-9", "10-12", "13-15", "16-17"), 
                   include.lowest = TRUE)
map_1000 <- county_choropleth(rain_1000,
                              title = "Hits for top 1000 Storm-County Pairs\nfor Rain > 75 mm",
                              legend = "Hits per County", num_colors = 6,
                              state_zoom = eastern_states)
map_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu", na.value = "white")
```

>>>>

Map of the count of county exposures to the top 1000 county-storm pairs by distance-based exposure, based on "exposed" = distance of 100 kilometers or less [GBA-- These are **awesome**. I think we want to tweak the color scale and the legend a bit so that they're consistent between the three plots showing the top 5000 storm-county pairs for the three metrics (distance, rain, and wind). That will make it easier to compare across the three maps, which is what we want readers to be able to do here.]:

@@

# distance_1000 <- distance_exposure %>%
#         arrange(desc(storm_dist)) %>%
#         group_by(fips) %>%
#         summarise(count = n()) %>%
#         rename(region = fips) %>%
#         mutate(region = as.numeric(region), count = as.numeric(count)) %>%
#         arrange(desc(count)) %>%
#         slice(1:1000)

distance_5000 <- distance_exposure %>%
        arrange(storm_dist) %>% # For distance, I don't think we want `desc`
        slice(1:5000) %>% # I think we need to slice out the top 1000 before 
                          # counting up by county. We want the top 1000
                          # county-storm pairs, not to count up the numbers for
                          # all storms within 100 km and then take the top 1000
                          # counties from that (which is what the old code did)
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))

distance_5000$value <- cut(distance_5000$count, c(0, 3, 6, 9, 12, 15, 17), 
                   labels = c("0-3", "4-6", "7-9", "10-12", "13-15", "16-17"), 
                   include.lowest = TRUE)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_5000 <- county_choropleth(distance_5000, 
                              title = "Hits for top 5000 Storm-County Pairs\nfor Distance < 100 km",
                              legend = "Hits per County", # num_colors = 7,
                              state_zoom = eastern_states)
map_dist_5000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu",
                                  na.value = "white")
```

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
# Get the rain-based exposure for all counties over the study period, 
# using a rain limit of 75 mm and a distance limit of 500 km
rain_exposure <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 75, dist_limit = 500,
                             days_include = c(-1, 0, 1))

# rain_1000 <- rain_exposure %>%
#         arrange(desc(tot_precip)) %>%
#         group_by(fips) %>%
#         summarise(count = n()) %>%
#         rename(region = fips) %>%
#         mutate(region = as.numeric(region), count = as.numeric(count)) %>%
#         arrange(desc(count)) %>%
#         slice(1:1000)
rain_5000 <- rain_exposure %>%
        arrange(desc(tot_precip)) %>%
        slice(1:5000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))

rain_5000$value <- cut(rain_5000$count, c(0, 3, 6, 9, 12, 15, 17), 
                   labels = c("0-3", "4-6", "7-9", "10-12", "13-15", "16-17"), 
                   include.lowest = TRUE)
map_5000 <- county_choropleth(rain_5000,
                              title = "Hits for top 5000 Storm-County Pairs\nfor Rain > 75 mm",
                              legend = "Hits per County", num_colors = 6,
                              state_zoom = eastern_states)
map_5000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGnBu",
                             na.value = "white")
```
